External validation

### 2020-09-29 diagnostics/README.Rmd
instructions for external validation

>>>>

We identified PJI within 90 days/2 years as either the primary or secondary reson for reoperation performed within this time frame, as recorded to SHAR, or if a relevant ICD-10/NOMESCO code was recorded during a hospitl visit/admission during this period.

We used regular expression to identify such codes:

```{r}
coder::hip_ae_hailer %>% 
  filter(group == "Infection")
```
